---
title: "Working with Docx Modifications"
author: ""
date: ""
output:
  word_document:
    reference_docx: ref02_addTextBox.docx
  html_document: default
---

***
```{r, echo=FALSE}
## The table below is needed to format the 
## header.  When the left column is empty, the 
## text in the right column turns blue and adds 
## an extra line space buffer in the final document.  
## I don't know how to fix this yet. 
## Also, the line break is needed between these 2 
## tables, or the formatting is affected.
```

-------- ------------------------------------------------------------------------
To:      Raquel Prado, Professor

         UC Santa Cruz
         
From:    Cheng-Han Yu, PhD student

         [Department of Applied Math and Statistics](https://www.soe.ucsc.edu/departments/applied-mathematics-statistics) 
         
         <cheyu@soe.ucsc.edu>
         
Subject: Final Report for Sarcopenia Measures from Trial 01-341 for the First of 
         2 Manuscripts
         
Date:    `r Sys.Date()`
-------- ------------------------------------------------------------------------

***

# Goal:

Main text of report goes here...

### Abstract
In this paper, we propose a efficient algorithm that detects which voxels in fMRI data are activated.

Inline Values in the Abstract
```{r, labeledChunkBeforeAbstract, echo=FALSE}
x <- 5 + 7
```
my inline value `r sum(x)` here.


# Introductiuon
stuff stuff stuff stuff stuff stuff stuff

The following is the code run in the abstract.
```{r, labeledChunkAfterAbstract, eval=FALSE}
<<labeledChunkBeforeAbstract>>
```
# Methods
Statistical algorithms Statistical algorithms Statistical algorithms

# Simulation Study
Simulation data and algorithm performance

# Data Analysis
Real human data analysis and comparison

# Discussions
Comparing different methods

# Conclusions
Here is the conclusion
